\documentclass[sigconf]{acmart}

\usepackage[english]{babel}

\usepackage[textsize=tiny]{todonotes}

% Copyright
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\settopmatter{printacmref=false, printccs=false, printfolios=true}

% DOI
\acmDOI{}

% ISBN
\acmISBN{}

%Conference
%\acmConference[Submitted for review to SIGCOMM]{}
%\acmYear{2018}
%\copyrightyear{}

%% {} with no args suppresses printing of the price
\acmPrice{}


\begin{document}
\title{An Architecture for Nanoservices}

%\titlenote{Produces the permission block, and copyright information}
%\subtitle{Extended Abstract}

\author{Paper \# XXX, XXX pages}
% \author{Firstname Lastname}
% \authornote{Note}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{Affiliation}
%   \streetaddress{Address}
%   \city{City} 
%   \state{State} 
%   \postcode{Zipcode}
% }
% \email{email@domain.com}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{X.et al.}

\begin{abstract}
Nanoservices are highly parallelizable, compute intensive applications with a cache resident working set and sub-microsecond response times. We believe that nanoservices will become popular in the future for two main reasons. One, Moore's Law is preventing increases in compute speed so we cannot rely on faster processors for performance gains. Two, many applications have inherent parallelizability that cannot be harnessed today because of large, unpredictable network delays and large overheads for small messages. In order to make nanoservices a reality, we need a new networking optimized compute platform. Thus, in this paper we present the Nanoservice Processing Unit (NanoPU) which has the following characteristics: (1) a fast path between the network and the core of the CPU to minimize average communication latency, (2) NIC driven thread scheduling to minimize tail response times, and (3) transport termination in the NIC to minimize communication overhead. We leave the third characteristic for future work. The NanoPU provides an order of magnitude lower average latency and XXX orders of magnitude lower tail latency than existing systems for nanoservice applications.
\end{abstract}

\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

\end{document}